---
title: "Egg dementia study"
output: github_document
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Required packages
pacs <- c("tidyverse", "readxl", "lubridate", "tableone", "gridExtra", "survival")
sapply(pacs, require, character.only = TRUE)

# Function to search variables
search_var <- function(df, pattern, ...) {
  loc <- grep(pattern, names(df), ...)
  if (length(loc) == 0) warning("There are no such variables")
  else return(data.frame(loc = loc, varname = names(df)[loc]))
}

# Medicare crosswalk ------------------------------------------------------

# Read crosswalk file: n = 70.968
crosswalk <- read_fwf("./Data/12172/2022/ssn_bene_xwalk_res000058038_req012172_2022.dat",
                      fwf_widths(c(9, 15, 1, 1, 1), c("ORIG_SSN", "BENE_ID", "SSN_MATCH", "SEX_MATCH", "DOB_MATCH")))

# Extract matched BENE_IDs
all_matched_bene_ids <- crosswalk %>% 
  filter(SSN_MATCH == 1)

# BENE_IDs of gender or DOB mismatch (to be removed)
mismatches <- crosswalk %>% 
  filter(SSN_MATCH == 1 & (SEX_MATCH == 0 | DOB_MATCH == 0)) %>%
  select(BENE_ID)
  
# There are two duplicates in BENE_IDs...
dup_BENE_IDs <- all_matched_bene_ids %>% 
  group_by(BENE_ID) %>% 
  summarize(n = sum(n())) %>% 
  filter(n > 1)

# There are 106 SSN duplicates 
dup_SSNs <- all_matched_bene_ids %>% 
  group_by(ORIG_SSN) %>% 
  summarize(n = sum(n())) %>% 
  filter(n > 1)

# BENE_IDs that need to be removed:
# Gender/DOB mismatch
# SSN/BENE_ID duplicates
exclude_BENE_IDs <- dup_BENE_IDs %>% 
  select(BENE_ID) %>% 
  union(all_matched_bene_ids %>% 
          filter(ORIG_SSN %in% dup_SSNs$ORIG_SSN) %>% 
          select(BENE_ID)
  ) %>% 
  union(mismatches)

# Medicare MSBF file ------------------------------------------------------

# Read MBSF Summary data on each year
# Data specification of MSBF files
fts_msbf <- read_excel("./Data/mbsf_format.xlsx")

# Create file names
year <- 2008:2020
fname <- paste0("./Data/12172/", year, "/mbsf_abcd_summary_res000058038_req012172_", year, ".dat")

# Read all MSBF files of 13 years
all_msbf <- fname %>% 
  lapply(\(x) read_fwf(x, fwf_widths(fts_msbf$length, fts_msbf$long_name))) %>% 
  lapply(\(x) anti_join(x, exclude_BENE_IDs)) %>% 
  setNames(year)

# Long format over years
all_msbf_long <- all_msbf %>% 
  do.call(rbind, .) %>% 
  arrange(BENE_ID, BENE_ENROLLMT_REF_YR)

# Medicare chronic condition file -----------------------------------------

# Read chronic conditions data on each year
fts_cc <- read_excel("./Data/mbsf_cc_format.xlsx")

# Create file names
year <- 2008:2020
fname <- paste0("./Data/12172/", year, "/mbsf_cc_summary_res000058038_req012172_", year, ".dat")

# Read all MSBF files of 13 years
all_cc <- fname %>% 
  lapply(\(x) read_fwf(x, fwf_widths(fts_cc$length, fts_cc$long_name))) %>% 
  lapply(\(x) anti_join(x, exclude_BENE_IDs)) %>% 
  setNames(year)

# Long format over years
all_cc_long <- all_cc %>% 
  do.call(rbind, .) %>% 
  arrange(BENE_ID, BENE_ENROLLMT_REF_YR)

# AHS-2 Medicare link file ------------------------------------------------

# AHS-2 analysis ID: N = 51,917
ahs <- read_csv("./Data/MedicareMatches2022.csv")

# There are 103 analysis IDs that appears twice
# There are 226 NULL values on analysis ID
# 104 analysis IDs (103 duplicates + NAs) to be removed
exclude_analysisIDs <- ahs %>% 
  group_by(AnalysisID) %>%
  tally() %>% 
  filter(n > 1) %>%
  select(AnalysisID)

# 432 rows removed (103 * 2 + 226)
# yielding 51,485 unique analysis ID (and unique Bene_IDs)
ahs_dup_removed <- ahs %>% anti_join(exclude_analysisIDs)

# AHS-2 data --------------------------------------------------------------

# N = 96,144
ahsdata <- read.csv("./Data/BaselineDataForMedicare20190531.csv", header=TRUE)
names(ahsdata) <- tolower(names(ahsdata))

# Remove those with missing analysis ID
# Calculate birth date and age in 2010
ahsdata <- 
  ahsdata %>% 
  filter(!is.na(analysisid)) %>% 
  mutate(mob         = ifelse(mob > 12, NA, mob),
         dob         = ifelse(dob > 31, NA, dob),
         yob         = ifelse(yob >= 9999, NA, yob),
         bdate       = as.Date(paste(yob, mob, dob, sep="-")),
         qreturndate = as.Date(qreturndate),
         agein       = as.numeric((qreturndate - bdate) / 365.242),
         age2010     = floor(as.numeric((as.Date("2010-12-31") - bdate) / 365.242)),
         age2011     = floor(as.numeric((as.Date("2011-12-31") - bdate) / 365.242)),
         deceased    = as.Date(deceased, format = "%Y-%m-%d"))

# Convert to numeric
ahsdata <- ahsdata %>% 
  mutate_at(vars(eggbetrf:educyou, incomeh:alcnow, cancer, anginay:a05q9, sleephrs:walkruna), 
            function(x) as.numeric(as.character(x)))

# Calculate BMI and BMI category
ahsdata <- ahsdata %>% 
  mutate(heighti = ifelse(heighti > 11, NA, heighti),
         bmi     = weight / (heightf * 12 + heighti) ^ 2 * 702,
         # bmicat  = cut(bmi, breaks = c(0, 18.5, 25, 30, Inf), right = FALSE),
         bmicat  = cut(bmi, breaks = c(0, 25, 30, Inf), right = FALSE),
         # bmicat  = factor(bmicat, labels = c("Underweight", "Normal", "Overweight", "Obese")))
         bmicat  = factor(bmicat, labels = c("Normal", "Overweight", "Obese")))

# Recode marital statas, education and sleep
ahsdata <- ahsdata %>% 
  mutate(marital   = recode(marital, "Never", "Married", "Married", "Married", "Div/Wid", "Div/Wid", "Div/Wid"),
         marital   = factor(marital, levels = c("Married", "Never", "Div/Wid")),
         educyou   = recode(educyou, "HS or less",   "HS or less",   "HS or less", 
                                     "Some college", "Some college", "Some college", 
                                     "Col grad+",    "Col grad+",    "Col grad+"),
         educyou   = factor(educyou, levels = c("HS or less", "Some college", "Col grad+")),
         educyou2  = relevel(educyou, ref = "Col grad+"),
         sleephrs  = recode(sleephrs, "<= 5 hrs", "<= 5 hrs", "<= 5 hrs", "6 hrs", "7 hrs",  
                                      "8 hrs", ">= 9 hrs", ">= 9 hrs", ">= 9 hrs"),
         sleephrs  = factor(sleephrs, levels = c("<= 5 hrs", "6 hrs", "7 hrs", "8 hrs", ">= 9 hrs")),
         sleephrs2 = relevel(sleephrs, ref = "7 hrs"))

# Dietary pattern
ahsdata$vegstat <- factor(ahsdata$vegstat, labels=c("Vegan", "Lacto-ovo",  "Semi", "Pesco", "Non-veg"))

# Physical activity
test <- ahsdata %>% 
  mutate(times    = walkrunf - 1,
         duration = recode(exeramt, 0, 5, 15, 25, 35, 45, 55, 60),
         minutes  = recode(walkruna, 5, 15, 25, 35, 45, 55, 60),
         distance = recode(walkrund, 0.25, 0.5, 1, 1.5, 2, 3, 4),
         vigofreq = ifelse(exerfreq - 2 < 0, 0, exerfreq - 2),
         ex4b4c   = times * distance,
         ex4b4d   = times * minutes,
         ex3a3b   = vigofreq * duration)

test <- test %>% 
  mutate(none = ifelse((ex3a3b == 0 & (walkrun == 2 | is.na(walkrun))) | 
                       (ex3a3b == 0 & times == 0) | (vigofreq == 0 & walkrun == 2), 1, 0),
         low  = ifelse((0 < ex3a3b & ex3a3b < 105) | (0 < ex4b4d & ex4b4d < 105) | (0 < ex4b4c & ex4b4c < 3), 1, 0),
         mid  = ifelse(ex3a3b >= 105 | (105 <= ex4b4d & ex4b4d < 175) | (3 <= ex4b4c & ex4b4c < 9), 1, 0),
         hi   = ifelse(ex4b4d >= 175 | ex4b4c >= 9, 1, 0))

ahsdata$exercise[test$none == 1] <- 1
ahsdata$exercise[test$low  == 1] <- 2
ahsdata$exercise[test$mid  == 1] <- 3
ahsdata$exercise[test$hi   == 1] <- 4
ahsdata$exercise <- factor(ahsdata$exercise, labels=c("None", "Low", "Moderate", "Vigorous"))
rm(test)

# AHS-2 dietary data ------------------------------------------------------

# N = 91099 obs, 105 variables
ahsdiet0 <- read.csv("./Data/MEDC_DMENT-FULL-20191008-0.csv", header = TRUE)

# N = 4498 obs, 105 variables
ahsdiet_ex <- read.csv("./Data/MEDC_DMENT-FULL-EXCLUDED-20191008-0.csv", header = TRUE)

# Concatenate two dfs
ahsdiet <- ahsdiet0 %>% bind_rows(ahsdiet_ex)
names(ahsdiet) <- tolower(names(ahsdiet))
ahsdiet$bmi <- NULL

# Merge AHS data with Medicare --------------------------------------------

# Extract data of the last seen: MSBF and CC files  
msbf_last_seen <- all_msbf_long %>%
  group_by(BENE_ID) %>% 
  slice(n())

cc_last_seen <- all_cc_long %>%
  group_by(BENE_ID) %>% 
  slice(n())

# Merge AHS data with Medicare
# Results in n = 44,384 subjects
ahs_medic <- msbf_last_seen %>% 
  inner_join(cc_last_seen %>% select(-BENE_ENROLLMT_REF_YR), by = "BENE_ID") %>%
  inner_join(ahs_dup_removed %>% 
               rename(BENE_ID = Bene_ID) %>% 
               mutate(analysisid = parse_number(AnalysisID)), by = "BENE_ID") %>% 
  inner_join(ahsdata, by = "analysisid") %>% 
  left_join(ahsdiet, by = "analysisid") %>% 
  ungroup()


# Apply inclusion/exclusion criteria --------------------------------------

# Remove if AGE_AT_END_REF_YR < 65 (n = 1545)
# Results in n = 42,839
ahs_medic <- ahs_medic %>% 
  filter(AGE_AT_END_REF_YR >= 65)

# Remove if qreturndate is missing -- 25 subjects
# Results in n = 42,814 subjects
ahs_medic <- ahs_medic %>% 
  filter(!is.na(qreturndate))

# Remove if BMI is missing (n = 1174) or extreme (n = 148)
# Resuts in n = 41,492
ahs_medic <- ahs_medic %>% 
  filter(bmi >= 16, bmi <= 60)

# Exclude missing kcal/diet (n = 97) or extreme kcal intake (n = 1039)
# Results in n = 40,356
ahs_medic <- ahs_medic %>% 
  filter(kcal > 500 & kcal < 4500)

# Identify alzheimer/dementia cases
ahs_medic <- ahs_medic %>% 
  mutate(ALZH_DEMEN_YN = ifelse(is.na(ALZH_DEMEN_EVER) & is.na(ALZH_EVER), 0, 1),
         ALZH_DEMEN_YN = factor(ALZH_DEMEN_YN, label = c("No", "Yes")))  

# Find prevalent cases
alz_diag_date <- ahs_medic %>% 
  filter(ALZH_DEMEN_YN == "Yes") %>% 
  mutate(ALZH_DEMEN_EVER = ymd(ALZH_DEMEN_EVER)) %>%
  mutate(DateDiff = interval(qreturndate, ALZH_DEMEN_EVER),
         DateDiff_days = as.numeric(DateDiff, 'days'), 
         DateDiff_months = as.numeric(DateDiff, 'months'), 
         DateDiff_years = as.numeric(DateDiff, 'years')) 

# Considering 6 months as a cut-off, there are 388 prevalent cases
prev_cases <- alz_diag_date %>% 
  filter(DateDiff_months< 6) %>% 
  select(BENE_ID, analysisid, ALZH_DEMEN_YN, qreturndate, ALZH_DEMEN_EVER, DateDiff_days, DateDiff_months, DateDiff_years)

# Exclude prevalent cases
# Yields n = 39,968 subjects
ahs_medic_inc <- ahs_medic %>% 
  anti_join(prev_cases, by = "analysisid") %>% 
  mutate(BENE_BIRTH_DT = ymd(BENE_BIRTH_DT),
         BENE_DEATH_DT = ymd(BENE_DEATH_DT),
         ALZH_DEMEN_EVER = ymd(ALZH_DEMEN_EVER))

# Need to exclude unverified deaths
# There are 21 unverified deaths
unverified_deaths <- ahs_medic_inc %>% 
  filter(!is.na(BENE_DEATH_DT)) %>%
  filter(is.na(VALID_DEATH_DT_SW)) %>% 
  select(analysisid)

# Exclude unverified deaths
# Yields n = 39,947
ahs_medic_inc <- ahs_medic_inc %>% 
  anti_join(unverified_deaths, by = "analysisid") 

# Define variables for models ---------------------------------------------

# Define ageout
# If ALZH_DEMEN_EVER exists (incident cases), the use this diag date
# If non-case and BENE_DEATH_DT exists, then use this date died (censored)
# Otherwise, use the end of BENE_ENROLLMT_REF_YR (year last seen)
ahs_medic_inc2 <- ahs_medic_inc %>% 
  mutate(
    age_last_seen = time_length(interval(BENE_BIRTH_DT, make_date(BENE_ENROLLMT_REF_YR, 12, 31)), "year"),
    ageout = case_when(
              ALZH_DEMEN_YN == "Yes" ~ time_length(interval(BENE_BIRTH_DT, ALZH_DEMEN_EVER), "year"),
              ALZH_DEMEN_YN == "No" & !is.na(BENE_DEATH_DT)  ~ time_length(interval(BENE_BIRTH_DT, BENE_DEATH_DT), "year"),
              ALZH_DEMEN_YN == "No" &  is.na(BENE_DEATH_DT)  ~ age_last_seen),
    fuyear = ageout - agein
  )

# Factor gender, categorize age into age groups, recode RTI race, smoking, and drinking
ahs_medic_inc2 <- ahs_medic_inc2 %>% 
  mutate(
    bene_sex_F = factor(SEX_IDENT_CD, labels = c("M", "F")),
    # bene_age_at_end_2008 = time_length(interval(BENE_BIRTH_DT, make_date(2008, 12, 31)), "year"),
    bene_age_at_end_2020 = time_length(interval(BENE_BIRTH_DT, make_date(2020, 12, 31)), "year"),
    # agecat     = cut(bene_age_at_end_2008, breaks = c(50, 60, 65, 70, 75, 80, 85, 120), right = FALSE),
    # agecat     = factor(agecat, labels = c("<60", "60-64", "65-69", "70-74", "75-79", "80-84", "85+")),
    agecat     = cut(bene_age_at_end_2020, breaks = c(65, 70, 75, 80, 85, 90, 95, 130), right = FALSE),
    agecat     = factor(agecat, labels = c("65-69", "70-74", "75-79", "80-84", "85-89", "90-94", "95+")),
    rti_race3  = recode(RTI_RACE_CD + 1, 3, 1, 2, 3, 3, 3, 3),
    rti_race3  = factor(rti_race3, labels = c("NH White", "Black", "Other")),
    smokenow   = ifelse(is.na(smokenow), 0, smokenow),
    smokecat   = ifelse(smokenow == 1, 2, ifelse(smoke > 1, 2, 1)),
    smokecat   = factor(smokecat, labels = c("Never", "Ever")),
    alcnow     = ifelse(is.na(alcnow), 0, alcnow),
    alccat     = ifelse(alcnow == 1, 2, ifelse(alcohol > 1, 2, 1)),
    alccat     = factor(alccat, labels = c("Never", "Ever")),
    vegstat2   = relevel(vegstat, ref = "Non-veg"))


# Co-morbidity ------------------------------------------------------------

# Prevalent comorbidity according to CMS
dzvars <- c("ami", "atrial_fib", "cataract", "chronickidney", "copd", "chf", "diabetes", "glaucoma",
            "hip_fracture", "ischemicheart", "depression", "osteoporosis", "ra_oa", "stroke_tia", 
            "cancer_breast", "cancer_colorectal", "cancer_prostate", "cancer_lung", "cancer_endometrial",
            "asthma", "hyperl", "hypert", "hypoth")
dzvars <- paste0(toupper(dzvars), "_EVER")

# Convert all comodidity ever variables to date
test <- ahs_medic_inc2 %>% 
  mutate(across(all_of(dzvars), ymd)) 

find_prevalence <- function(var, data, start){
  cc_var <- data[[var]]
  strtdt  <- data[[start]]
  out <- ifelse(cc_var <= strtdt, 1, 0)
  out <- ifelse(is.na(cc_var), 0, out)
  return(out)
}

dzdf <- as.data.frame(lapply(dzvars, find_prevalence, data = test, start = "qreturndate"))
names(dzdf) <- paste0(dzvars, "_YN")
dzdf <- as_tibble(dzdf)

dzdf <- dzdf %>% 
  mutate(como_depress  = DEPRESSION_EVER_YN,
         como_diabetes = DIABETES_EVER_YN,
         como_kidney   = CHRONICKIDNEY_EVER_YN,
         como_hypoth   = HYPOTH_EVER_YN,
         como_cancers  = ifelse(rowSums(.[grep("CANCER_", names(.))]) > 0, 1, 0),
         como_cvd      = ifelse(rowSums(.[grep("AMI|ATRIAL|CHF|ISCHEMIC|STROKE", names(.))]) > 0, 1, 0),
         como_disab    = ifelse(rowSums(.[grep("CATARACT|GLAU|HIP|OSTEO|RA_OA", names(.))]) > 0, 1, 0),
         como_hthl     = ifelse(rowSums(.[grep("HYPERT|HYPERL",  names(.))]) > 0, 1, 0),
         como_resp     = ifelse(rowSums(.[grep("COPD|ASTHMA",  names(.))]) > 0, 1, 0)) %>% 
  mutate_at(vars(starts_with("como_")), factor, labels = c("No", "Yes")) %>% 
  select(starts_with("como_"))

ahs_medic_inc2 <- ahs_medic_inc2 %>% 
  bind_cols(dzdf)

modelvars <- c("bene_age_at_end_2020", 
               "bene_sex_F", 
               "rti_race3", 
               "marital", 
               "educyou", 
               "vegstat", 
               "bmi", 
               "exercise", 
               "sleephrs", 
               "smokecat", 
               "alccat", 
               "como_depress",
               "como_disab", 
               "como_diabetes", 
               "como_cvd", 
               "como_hthl", 
               "como_resp", 
               "como_kidney", 
               "como_hypoth", 
               "como_cancers",
               "meat_gram",
               "fish_gram",
               "eggs_gram",
               "dairy_gram"
)

# After excluding missing on covariates
# there are 36,549 subjects
complete_cases <- ahs_medic_inc2 %>% 
  select(analysisid, all_of(modelvars)) %>% 
  filter(complete.cases(.)) %>% 
  select(analysisid)

ahs_medic_inc2 <- ahs_medic_inc2 %>% 
  inner_join(complete_cases, by = "analysisid")

# dietary variables -------------------------------------------------------

# Food group variables
# Energy-adjust with zero partition
source("myfunc.R")
ahs_medic_inc2$meat_gram_ea      <- kcal_adjust(meat_gram,  kcal, data = ahs_medic_inc2, log = TRUE)
ahs_medic_inc2$fish_gram_ea      <- kcal_adjust(fish_gram,  kcal, data = ahs_medic_inc2, log = TRUE)
ahs_medic_inc2$eggs_gram_ea      <- kcal_adjust(eggs_gram,  kcal, data = ahs_medic_inc2, log = TRUE)
ahs_medic_inc2$dairy_gram_ea     <- kcal_adjust(dairy_gram, kcal, data = ahs_medic_inc2, log = TRUE)
ahs_medic_inc2$nutsseeds_gram_ea <- kcal_adjust(nutsseeds_gram, kcal, data = ahs_medic_inc2, log = TRUE)

# Quartiles for egg, dairy and nuts/seeds
ea_diet_vars <- c("eggs_gram_ea", "dairy_gram_ea", "nutsseeds_gram_ea")
get_percentile <- function(var, data = ahs_medic_inc2) cutQ(data[[var]], na.rm = TRUE, p = 0:4/4)
test <- lapply(ea_diet_vars, get_percentile)
names(test) <- paste0(ea_diet_vars, "_4")
ahs_medic_inc2 <- cbind(ahs_medic_inc2, test)
rm(test)

ahs_medic_inc2 <- ahs_medic_inc2 %>% 
  mutate(meat_gram_ea_4 = cut(meat_gram_ea, breaks = c(-Inf, 0, 11, 32, Inf), right = TRUE), 
         fish_gram_ea_4 = cut(fish_gram_ea, breaks = c(-Inf, 0,  8.6, 17.2, Inf), right = TRUE))

```

## Aim

* Association between egg intake and the incidence of dementia/Alzheimer’s disease in the AHS-2 cohort linked with Medicare data

## Datasets

* Medicare data
  * For details regarding Medicare data, see [AHS-2 Medicare Linkage](https://github.com/keijioda/ahs_medicare_linkage/blob/main/summary.md) repository.
  
  * Master Beneficiary Summary File (MBSF), 2008-2020
    * Contains beneficiary characteristics and enrollment information
    
  * Chronic Conditions file (CC), 2008-2020
    * Contains the first occurrence date of 27 specific chronic conditions
    * Used to identify prevalent/incident cases of dementia and/or Alzheimer's disease and
    * to identify comorbidities
    
  * Both files include n = 44,585 unique subjects across years, after excluding 
    * Gender/DOB mismatch with AHS-2 data
    * Dupulicate beneficiary IDs and SSNs

* AHS-2, n = 96,144
  * Baseline data
  * Dietary data
  
* After merging Medicare and AHS-2 data, there were n = 44,359 subjects.

## Inclustion/exclusion criteria

* Medicare beneficiaries who did not reach the age of 65 between 2008 and 2020 (e.g., younger beneficiaries with disabilities or end-stage renal disease) were excluded (n = 1545), resulting n = 42,814.

* n = 1322 subjects with missing BMI or extreme BMI (<16 or >60), according to AHS questionnaire, were excluded (n = ), resulting n = 41,492.

* n = 1136 subjects with extreme calorie intake (<500 or >4500 kcal) were excluded, resulting n = 40,356.

* Prevalent cases of dementia and/or Alzheimer's disease
  * If the first diagnosis was made before AHS-2 enrollment or within 6 months after the enrollment, consider it as a prevalent case
  * n = 388 such prevalent cases were excluded, resulting n = 39,968 subjects
  
* Unverified dates of deaths
  * Medicare data include a variable (`VALID_DEATH_DT_SW`) indicating whether a beneficiary's day of death has been verified by the Social Security Administration or the Railroad Retirement Board.
  * There were 21 unverified death dates. Excluding these resulted n = 39,947.

* Missing values in covariates
  * There were n = 3398 subjects who has at least one missing value on covariates (such as marital status, education, exercise level, sleep hours, smoking and alcohol use, all of them come from AHS questionnaire). These subjects were excluded, resulting in n = 36,549.

## Dietary variables 

* This section is to be completed
* Adjusting for energy
<!-- * For each ??, its dietary intake was energy-adjusted by the residual method, while partitioning zero intake ([Jaceldo-Siegl et al., 2011](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3433053/)). Due to its highly right-skewed distribution, non-zero intake was log-transformed before being regressed on the total energy intake. Residuals were added by the mean of log and then back-transformed to obtain energy-adjusted dietary intake. Energy-adjusted dietary intake was added with (unadjusted) supplement intake to form energy-adjuste total intake. -->
* Food groups, divided into 4 intake levels
  
## Descriptive table

```{r descriptive_stratified, echo = FALSE}
# Variables to be included
tablevars <- c("agecat", 
               # "bene_age_at_end_2008", 
               "bene_age_at_end_2020", 
               "bene_sex_F", 
               "rti_race3", 
               "marital", 
               "educyou", 
               "vegstat", 
               "bmicat", 
               "bmi", 
               "exercise", 
               "sleephrs", 
               "smokecat", 
               "alccat", 
               "como_depress",
               "como_disab", 
               "como_diabetes", 
               "como_cvd", 
               "como_hthl", 
               "como_resp", 
               "como_kidney", 
               "como_hypoth", 
               "como_cancers",
               "meat_gram_ea_4",
               "fish_gram_ea_4",
               "eggs_gram_ea_4",
               "dairy_gram_ea_4"
               )

tablevars %>% 
  CreateTableOne(strata = "ALZH_DEMEN_YN", data = ahs_medic_inc2, addOverall = TRUE) %>% 
  print(showAllLevels = TRUE) %>% 
  kableone()  
```

